---
title: "Simulation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
 fig.align = "center",
 fig.width = 7,
fig.height = 5
)
```

```{r setup}
library(BayesCER)
library(tidyverse)

data("sim_data_result", package = "BayesCER")
```

```{r, include=FALSE}
N_vec <- c(10)
alpha_vec <- c(0.2)
```

## Simulation study

We compare the empirical Bayes and Gibbs sampling approaches implemented in
`BayesCER`. The simulation results are precomputed and included with the
package, so that the simulations do not need to be
rerun when building the vignette.

The performance of the two approaches is assessed in terms of the estimation
error for the representative graph and the scale parameter, as well as the
accuracy of graph-level summary statistics.


```{r normalized Hamming error for C}
ggplot(
  sim_data_result,
  aes(
    x = as.factor(n),
    y = discrepancy_C_hat_norm,
    fill = method
  )
) +
  geom_boxplot(
    aes(colour = after_scale(colorspace::darken(fill, 0.2))),
    position = position_dodge(width = 0.8),
    outlier.shape = NA,
    linewidth = 0.3,
    show.legend = c(colour = FALSE, fill = TRUE)
  ) +
  stat_boxplot(
    aes(colour = method),
    geom = "errorbar",
    position = position_dodge(width = 0.8),
    width = 0.2,
    show.legend = FALSE
  ) +
  stat_summary(
    fun = median,
    geom = "point",
    position = position_dodge(width = 0.8),
    size = 1.2,
    colour = "black",
    show.legend = FALSE
  ) +
  labs(
    x = "Sample size n",
    y = "",
    fill = "Method",
     title = bquote(
    "Normalized Hamming error " ~ d[H](C, hat(C))/M ~
    " for " ~ N == .(N_vec) ~ " and " ~ alpha == .(alpha_vec)
  )
    # title = paste0(
    #   expression("Normalized Hamming error " ~ d[H](C, hat(C))/M), 
    #   "for N = ", N_vec, "and ", expression(alpha), " = ",  alpha_vec)
  ) +
  theme_bw() +
  theme(
    panel.spacing.x = unit(0, "mm"),
    plot.margin = margin(rep(1, 4), unit = "mm"),
    strip.text = element_text(size = 14),
    axis.text = element_text(size = 14),
    strip.text.y.right = element_text(size = 14),
    strip.text.x.top = element_text(size = 14),
    axis.title.x = element_text(size = 14)
  )
```

```{r absolute error for alpha }
ggplot(
  sim_data_result,
  aes(
    x = as.factor(n),
    y = discrepancy_alpha_hat,
    fill = method
  )
) +
  geom_boxplot(
    aes(colour = after_scale(colorspace::darken(fill, 0.2))),
    position = position_dodge(width = 0.8),
    outlier.shape = NA,
    linewidth = 0.3,
    show.legend = c(colour = FALSE, fill = TRUE)
  ) +
  stat_boxplot(
    aes(colour = method),
    geom = "errorbar",
    position = position_dodge(width = 0.8),
    width = 0.2,
    show.legend = FALSE
  ) +
  stat_summary(
    fun = median,
    geom = "point",
    position = position_dodge(width = 0.8),
    size = 1.2,
    colour = "black",
    show.legend = FALSE
  ) +
  labs(
    title = bquote(
    "Absolute error " ~ abs(alpha - hat(alpha)) ~
    " for " ~ N == .(N_vec) ~ " and " ~ alpha == .(alpha_vec)),
    x = "Sample size n",
    y = "",
    fill = "Method"
  ) +
  theme_bw() +
  theme(
    panel.spacing.x = unit(0, "mm"),
    plot.margin = margin(rep(1, 4), unit = "mm"),
    strip.text = element_text(size = 14),
    axis.text = element_text(size = 14),
    strip.text.y.right = element_text(size = 14),
    strip.text.x.top = element_text(size = 14),
    axis.title.x = element_text(size = 14)
  )
```
```{r ecc }
ggplot(
  sim_data_result,
  aes(
    x = as.factor(n),
    y = ecc_hat,
    fill = method
  )) +
  geom_boxplot(
    aes(colour = after_scale(colorspace::darken(fill, 0.2))),
    position = position_dodge(width = 0.8),
    outlier.shape = NA,
    # colour = NA,
    linewidth = 0.3,
    show.legend = c(colour = FALSE, fill = TRUE)
  ) +
  stat_boxplot(
    aes(colour = method),
    geom = "errorbar",
    position = position_dodge(width = 0.8),
    width = 0.2,
    show.legend = FALSE
  ) +
  stat_summary(
    fun = median,
    geom = "point",
    position = position_dodge(width = 0.8),
    size = 1.2,
    colour = "black",
    show.legend = FALSE
  ) +
  geom_hline(
  aes(
    yintercept = ecc_true,
    linetype = "True value",
    colour = "True value"
  )
) +
scale_linetype_manual(
  name = NULL,
  values = c("True value" = "dashed")
) +
scale_colour_manual(
  values = c("True value" = "black"),
  guide = "none"
) +
  labs(
    title = bquote(
    "Approximate expected clustering coefficient" ~
    " for " ~ N == .(N_vec) ~ " and " ~ alpha == .(alpha_vec)),
    x = "Sample size n", y = "", fill = "Method") +
  theme_bw() +
  theme(
    panel.spacing.x = unit(0, "mm"),
    plot.margin = margin(rep(1,4), unit="mm"),
    strip.text = element_text(size=14),
    axis.text = element_text(size=14),
    strip.text.y.right  = element_text(size = 14),
    strip.text.x.top    = element_text(size = 14),
    axis.title.x = element_text(size = 14)
  )
```

```{r eed }
ggplot(
  sim_data_result,
  aes(
    x = as.factor(n),
    y = total_degree_norm,
    fill = method
  )) +
  geom_boxplot(
    aes(colour = after_scale(colorspace::darken(fill, 0.2))),
    position = position_dodge(width = 0.8),
    outlier.shape = NA,
    # colour = NA,
    linewidth = 0.3,
    show.legend = c(colour = FALSE, fill = TRUE)
  ) +
  stat_boxplot(
    aes(colour = method),
    geom = "errorbar",
    position = position_dodge(width = 0.8),
    width = 0.2,
    show.legend = FALSE
  ) +
  stat_summary(
    fun = median,
    geom = "point",
    position = position_dodge(width = 0.8),
    size = 1.2,
    colour = "black",
    show.legend = FALSE
  ) +
  geom_hline(
  aes(
    yintercept = total_degree_true_norm,
    linetype = "True value",
    colour = "True value"
  )
) +
scale_linetype_manual(
  name = NULL,
  values = c("True value" = "dashed")
) +
scale_colour_manual(
  values = c("True value" = "black"),
  guide = "none"
) +
  labs(
    title = bquote(
    "Expected edge density" ~
    " for " ~ N == .(N_vec) ~ " and " ~ alpha == .(alpha_vec)),
    x = "Sample size n", y = "", fill = "Method") +
  theme_bw() +
  theme(
    panel.spacing.x = unit(0, "mm"),
    plot.margin = margin(rep(1,4), unit="mm"),
    strip.text = element_text(size=14),
    axis.text = element_text(size=14),
    strip.text.y.right  = element_text(size = 14),
    strip.text.x.top    = element_text(size = 14),
    axis.title.x = element_text(size = 14)
  )
```

